### 2018-02-18 doc/manuscript.Rmd
fix up front matter, title, authors

---
bibliography: 
    - /home/luke/Documents/bibliography/bib/bib-db/tagDiabetes.bib
    - /home/luke/Documents/bibliography/bib/bib-db/myrefs.bib
    - /home/luke/Documents/bibliography/bib/bib-db/methods.bib
csl: /home/luke/Documents/bibliography/styles/vancouver.csl
output: fost::jlr_manuscript
---

@@

Title: Specific clusters of fatty acids within the serum triacylglyceride fraction 
associate with the pathogenesis of type 2 diabetes

Author: Luke W. Johnston, MSc (1); Zhen Liu, PhD (1); Ravi Retnakaran, MD
(3,4); Bernard Zinman, MD (3,4); Adria Giacca, PhD (5); Stewart B. Harris, MD (2); 
Richard P. Bazinet, PhD (1); and Anthony J. Hanley, PhD (1,3,6)

<!-- During time of study. -->
Affiliation:

>>>>

---
bibliography: 
    - /home/luke/Documents/bibliography/bib/bib-db/tagDiabetes.bib
    - /home/luke/Documents/bibliography/bib/bib-db/myrefs.bib
    - /home/luke/Documents/bibliography/bib/bib-db/methods.bib
    - /home/luke/Documents/site/cv/_includes/work.bib
csl: /home/luke/Documents/bibliography/styles/vancouver.csl
output: fost::jlr_manuscript
---

@@

Title (109 / 110 characters): 
Clusters of fatty acids in serum triacylglyceride fraction associate with the
pathogenesis of type 2 diabetes

Authors: Luke W. Johnston, PhD (1); Zhen Liu, PhD (1); Ravi Retnakaran, MD
(3,4); Bernard Zinman, MD (3,4); Adria Giacca, PhD (5); Stewart B. Harris, MD (2); 
Richard P. Bazinet, PhD (1); and Anthony J. Hanley, PhD (1,3,6)

Institutions:
